Consumer Price Index Analysis and Forecasting

### 2022-10-28 paper/paper.tex
change figures
changes to pdf

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[table]{xcolor}
\usepackage{pgfplots}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics[scale=0.68]{../figs/cpi.pdf}
    \caption{Denmark CPI (All Items)}
    \label{fig:cpi}
\end{figure}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics[scale=0.68]{../figs/trend.pdf}
    \caption{Trend fitting}
    \label{fig:trend}
\end{figure}

The results suggest that the time series's trend is better described by the LOWESS approach as seen in Table \ref{fig:trend} and Figure \ref{fig:trend}\footnote{Graphing period was shortened for better visualization}. The linear and quadratic trends, due to their low-order nature and usage of the global structure of the data, are not sensitive to oscillations and thus are only able to give a rough approximation. The Moving Average and LOWESS fittings, on the other hand, rely on the local structure of the data and are non-linear, allowing them tend to these oscillations. LOWESS yields a better approximation as it performs multiple local (weighted) regression instead of averages, thus being more sensitive to outliers.

\begin{figure*}[hbtp]
    \centering
    \includegraphics[scale=0.7]{../figs/season.pdf}
    \caption{The frequency spectrum (right), the trendless timeseries and the seasonality fitting (top left), the estimate erratic component (bottom left).}
    \label{fig:season}
\end{figure*}

@@

\begin{figure*}[hbtp]
    \centering
    \includegraphics[scale=0.7]{../figs/differencing.pdf}
    \caption{Stationarity by differencing}
    \label{fig:differencing}
\end{figure*}

\begin{figure*}[hbtp]
    \centering
    \includegraphics[scale=0.7]{../figs/acs_diff.pdf}
    \caption{Correlogram of first-order differencing (top) and seasonal differencing (bottom)}
    \label{fig:acs_diff}
\end{figure*}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[table]{xcolor}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics{../figs/cpi.pdf}
    \caption{Denmark CPI (All Items)}
    \label{fig:cpi}
\end{figure}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics{../figs/trend.pdf}
    \caption{Trend fitting}
    \label{fig:trend}
\end{figure}

The results suggest that the time series's trend is better described by the LOWESS approach as seen in Table \ref{fig:trend} and Figure \ref{fig:trend}. The linear and quadratic trends, due to their low-order nature and usage of the global structure of the data, are not sensitive to oscillations and thus are only able to give a rough approximation. The Moving Average and LOWESS fittings, on the other hand, rely on the local structure of the data and are globally non-linear, allowing them to tend to these oscillations. LOWESS yields a better approximation as it performs multiple local (weighted) regression instead of averages, thus being more sensitive to outliers.

\begin{figure*}[hbtp]
    \centering
    \includegraphics{../figs/season.pdf}
    \caption{The frequency spectrum (right), the trendless timeseries and the seasonality fitting (top left), the estimate erratic component (bottom left).}
    \label{fig:season}
\end{figure*}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics{../figs/differencing.pdf}
    \caption{Stationarity by differencing}
    \label{fig:differencing}
\end{figure}

\begin{figure}[hbtp]
    \centering
    \includegraphics{../figs/acs_diff.pdf}
    \caption{Correlogram of first-order differencing (top) and seasonal differencing (bottom)}
    \label{fig:acs_diff}
\end{figure}
